SPARQL on the Open, Decentralised Web

### 2016-07-25 dissertation/problems.tex
improve wording #6

To understand whether a result from a study on for example, performance is
valid, an empirical study must be conducted, as a SPARQL system is
generally too complex to be evaluated solely by formal
methods. Conventionally, one or more benchmarks have been used for
this purpose, and there exists a number of such
benchmarks. Unfortunately, due to this complexity, they have to test a
very large number of parameters, but are unable to do that, and they
may also oversimplify the test by attempting to neutralise certain
optimisation techniques. Further, they have no structured approach to
investigate flaws in the benchmark itself, and have no meaningful
summary statistics that can be used to understand the overall
performance. While one may standardise benchmarks, doing so makes it
impossible to test assertions that are outside of that standard.

>>>>

To understand whether a result from a study on for example,
performance is valid, an empirical study must be conducted, as a
SPARQL system is generally too complex to be evaluated solely by
formal methods. Conventionally, one or more benchmarks have been used
for this purpose, and there exists a number of such
benchmarks. Unfortunately, due to the complexity of the systems under
evaluation, benchmarks have to test a very large number of parameters,
which is methodologically beyond their reach. They may also
oversimplify the test by attempting to neutralise certain optimisation
techniques. Further, they have no structured approach to investigate
flaws in the benchmark itself, and have no meaningful summary
statistics that can be used to understand the overall
performance. While one may standardise benchmarks, doing so makes it
impossible to test assertions that are outside of that standard.
